Structured Versus Decorated Cospans

### 2020-11-19 cospans.tex
few leftover edits

Since both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, 
{\chris in progress}

as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal. First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$. The diagrams utilizing these maps that are required to commute do so trivially.

@@

>>>>

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially

 First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$. The diagrams utilizing these maps that are required to commute do so trivially.

@@

DEFINITION OF SYMMETRIC MONOIDAL ISOMORPHISM, BRIEFLY?
